### 2016-03-14 WRITEUP/Lensmodel.tex
fix alignment

\begin{figure}[tbph]
\centering
\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.eps}
\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
\caption{
Pseudo observed 0th moment map in the lens plane. (left)
Pseudo 0th moment map in the source plane. (right)
\label{fig:}}
\end{figure}

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.eps}
\caption{
velocity gradient of the lens model in the lens plane (left), source plane (right).
\label{fig:}}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
+ Compare our lens model parameters on the mass distribution of the lensing
galaxy with literature (specifically SIE model in C06)
	- C06: SIE model shows position of lensing mass is offset by (-0.015",
-0.041" from obs. (i.e. light centroid)); PA = -73.6, ellipticity = 0.45,
theta_R = 1.84" +/- 0.01 
	- Our model lens parameters (median):
		- file: WRITEUP/MedianLensModelParams.txt
		- lensing gal. position is consistent with C06, 
		- Einstein radius: consistent with C06
		- PA: consistent within errors
		- Axial ratio: consistent within errors
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[tbph]
\centering
\includegraphics[width=0.50\textwidth]{../Figures/Pseudointegrated_datamodel.ep
s}
\includegraphics[width=0.50\textwidth]{../Figures/SourcesPlane.png}
\caption{
Pseudo observed 0th moment map in the lens plane. (left)
Pseudo 0th moment map in the source plane. (right)
\label{fig:}}
\end{figure}

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{../Figures/PseudoRGB_Lensed_SB_double.ep
s}
\caption{
velocity gradient of the lens model in the lens plane (left), source plane
(right).
\label{fig:}}
\end{figure*}

### 2016-03-14 WRITEUP/Obs.tex
place holder for paper
fix alignment

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 0.655BLAH
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the redshifted frequency of $\nu_{\rm obs}$ = 
 BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under excellent / GOOD? 
%2 mm
weather conditions in the C and D array configurations, respectively. The 2 mm receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line and the underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing a correlator setup providing an effective bandwidth of 3.16 GHz and spectral resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time 
after discarding unusable visibility data.
% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp), 1124-106(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186 (phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and MWC349 was observed as the primary
absolute flux calibrator for C array observations.
The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes for
pointing, secondary amplitude, and phase calibration, and 3C279 was observed as the primary
absolute flux calibrator for D array observations.
1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array observations, respectively, yielding $\lesssim
$15\% calibration accuracy.

@@

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 3C273 FG
% 3C279 Bandpass
% mars flux
% after flagging: Total observing time is  1.48 hours, checked with uvindex
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH 
 were carried out using the Combined Array for Research in Millimeter-wave Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz (BLAH mm) (Program ID: cf0098; PI: D. Riechers).
observations were carried out on 2014 February 17 under good 3 mm weather conditions in the D array configurations. The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 12.5 MHz ($\sim$17BLAH km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz; this resulted in 1.5 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.

@@

The nearby radio quasar BLAH was observed every BLAH minutes for
pointing, amplitude, and phase calibration, and BLAH was observed as the primary
absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding $\sim
$15\% calibration accuracy.
The AIPS package was used to calibrate and analyze the visibility data which are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image. The final rms noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.
%
%\section{Continuum}
%%90.6797 GHz
%% VLA sigma =  Jy
%
%no continuum detection..
%Averaging over all the line-free channels, we did not detect the radio continuum down to 2$\sigma$ of blah mJy at an averaged frequency of $\nu_{cont}$ = 90.7 GHz.
%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.80\textwidth]{../OverlayFig/ContPanel}
%\caption{Left: Contours of the CARMA 90.7 GHz continuum emission (red) in the foreground radio galaxy 3C220.3 overlaid on the image and contours of the VLA 6 GHz continuum emission (lime). The rms in the VLA 6 GHz continuum image is $\sigma$ = 0.0641 mJy beam$^{-1}$. The synthesized beam size is 0$\farcs$596 $\times$ 0$\farcs$229, at P.A. 75.79$\degr$. Lime contour levels start at $\pm$4$\times\sigma$ = x mJy beam$^{-1}$ and increment at steps of $\pm$2$\sigma$ for the VLA data; red contour levels start at $\pm$2$\sigma$, incrementing at steps of $\pm$1$\sigma$ = 0.24 mJy beam$^{-1}$.
%Right:
%Contour map of the 90.7 GHz continuum emission. The beam size is 16\farcs67$\pm
%$0\farcs69 $\times$ 7\farcs17$\pm$1\farcs60, at P.A. = -57.9$\degr$. The contour levels start at $\pm$2$\sigma$ and increment at steps of $\pm$1$\sigma$ =0.5 mJy beam$^{-1}$.\label{fig:cont}}
%\end{figure*}
%
%
%\section{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
%%- ! Parameters and Errors:
%%- ! MFIT%PAR[01]   10.289188385009766        1.7304190817956480
%%- ! MFIT%PAR[02]   51.276344299316406        29.649510734050978
%%- ! MFIT%PAR[03]   147.87234497070312 * 2.355        30.276954728539007
%%- ! MFIT%PAR[04]  0.34727144241333008       0.22560386117523606
%%- channel [, ]
%%- velocity range [,] km/s
%%- Integrated line flux =
%%- rms =
%
%%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
%We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939+8315. We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:mom0}, yielding peak flux density of 10.3 $\pm$ 1.7 mJy, the FWHM of the Gaussian fit is 541.65 $\pm$ 31.91 km s$^{-1}$. The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, where the synthesized beam size of the SMA observation is 1\farcs42$\times$1\farcs16, at P.A. -34.0\degr. Since the angular resolution of our CO measurement is 13$\farcs$57 $\pm$ 1\farcs4 $\times$ 5\farcs77 $\pm$ 3\farcs1, the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is therefore spatially unresolved. We construct the velocity-integrated (moment-0) map of the CO($J$ = 3 $\rightarrow$ 2) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux is 14.6 $\pm$ 0.9 Jy km s$^{-1}$.
%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.8\textwidth]{../OverlayFig/CO32mom0}
%\includegraphics[width=0.65\textwidth]{../OverlayFig/2.685bin2_arcNS_further_Sblob}
%\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$2$\sigma$, incrementing at
%steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 5\farcs77, at P.A. = -60.67$\degr$.
%Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (lime contours) with $\sigma$=0.836951 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34.0\degr, as shown in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam size of the CARMA data, hence the CO($J$ = 3 $\rightarrow$ 2) detection is spatially unresolved.
%Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy beam$^{-1}$ (before continuum
%subtraction), and the integrated line flux over linewidth of $\sim$500 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
%(after continuum subtraction).  \label{fig:mom0}}
%\end{figure*}
%
%No significant continuum emission is detected from the line-free region down to a 1$\sigma$ limit of blah mJy. Neither CO(3-2) emission nor continuum emission are seen in the map near the NIR positions.
%
%at $z$ = 2.685, 1$\arcsec \sim$ 8.1 kpc
%

>>>>

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
redshifted frequency of $\nu_{\rm obs}$ = 
 BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
%2 mm
weather conditions in the C and D array configurations, respectively. The 2 mm
receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
and the 
underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing
a correlator setup providing an effective bandwidth of 3.16 GHz and spectral 
resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time

after discarding unusable visibility data.
% D: 1.5 hours; 1055+018 , 3C279 (RF, fixed flux), 1127-145 (phase/amp),
1124-106(ditto)
% C: 2.2 hours; MWC349 (fixed flux), 1055+018 (RF = bandpass), 1124-186
(phase/amp), 1127-145 (ditto)
% total: 3.75 hours
%For both tracks, 
The nearby quasars 1127$-$145 and 1124$-$186 were observed every BLAH minutes
for
pointing, secondary amplitude, and phase calibration, and MWC349 was observed
as the primary
absolute flux calibrator for C array observations.
The nearby quasars 1127$-$145 and 1124$-$106 were observed every BLAH minutes
for
pointing, secondary amplitude, and phase calibration, and 3C279 was observed as
the primary
absolute flux calibrator for D array observations.
1055$+$018 and 3C279 were observed as bandpass calibrators for C and D array
observations, respectively, yielding $\lesssim
$15\% calibration accuracy.

@@

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 3C273 FG
% 3C279 Bandpass
% mars flux
% after flagging: Total observing time is  1.48 hours, checked with uvindex
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH 
 were carried out using the Combined Array for Research in Millimeter-wave
Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz
(BLAH 
mm) (Program ID: cf0098; PI: D. Riechers).
observations were carried out on 2014 February 17 under good 3 mm weather
conditions in the D array configurations. The 3 mm receivers were used to cover
the 
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($
\sim$17BLAH km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 1.5 hours of 15 antenna-equivalent on-source time after
discarding 
unusable visibility data.

@@

The nearby radio quasar BLAH was observed every BLAH minutes for
pointing, amplitude, and phase calibration, and BLAH was observed as the
primary
absolute flux calibrator. BLAH were observed as bandpass calibrators, yielding
$\sim
$15\% calibration accuracy.
The AIPS package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 2$\farcs$6 $\times$ 2\farcs2 for the continuum image. The final
rms 
noise is $\sigma$ = 0.68 Jy km s$^{-1}$ beam$^{-1}$.

### 2016-03-14 WRITEUP/Results.tex
fix alignment

\section{CO($J$ = 3 $\rightarrow$ 2) line emission}
%- ! Parameters and Errors:
%- ! MFIT%PAR[01]  
%- ! MFIT%PAR[02]  
%- ! MFIT%PAR[03]  
%- ! MFIT%PAR[04]  
%- channel [, ]
%- velocity range [,] km/s
%- Integrated line flux =
%- rms =

%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.

We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background galaxies in RXJ1131-1231. 
We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:CO32mom0}, 
yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit is BLAH $\pm$ BLAH km s$^{-1}$.

%No significant continuum emission is detected from the line-free region down to a 1$\sigma$ limit of blah mJy.

\section{CO($J$ = 2 $\rightarrow$ 1) line emission}
We detect dynamically resolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background galaxies in RXJ1131-1231.

We construct the velocity-integrated (0th moment) map of the CO($J$ = 2 $\rightarrow$ 1) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 2 $\rightarrow$ 1) line flux is BLAH $\pm$ BLAH Jy km s$^{-1}$.

% upper limit on other lines 
% in the background source -- H2CO

% in the foreground galaxy -- H2CO, HNC (J=2-1)
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{
0th Moment map of CO(2-1) emission on HST F555W.
Spectrum. Velocity scale w.r.t z=0.655
 \label{fig:CO21mom0}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
\caption{
1st and 2nd order moments
 \label{fig:}}
\end{figure}

@@

%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.8\textwidth]{}       % figures are in ../Figures/ for now, before we decided which ones will definitely go into paper
%\includegraphics[width=0.65\textwidth]{}
%\caption{
% \label{fig:}}
%\end{figure*}

@@

%
%\begin{figure*}[tbph]
%\centering
%\includegraphics[width=0.80\textwidth]{}
%\caption{Left: Contours of the CARMA BLAH GHz continuum emission (red) in the foreground radio galaxy 3C220.3 overlaid on the image and contours of the VLA 6 GHz continuum emission (lime). The rms in the VLA 6 GHz continuum image is $\sigma$ = 0.0641 mJy beam$^{-1}$. The synthesized beam size is 0$\farcs$596 $\times$ 0$\farcs$229, at P.A. 75.79$\degr$. Lime contour levels start at $\pm$4$\times\sigma$ = x mJy beam$^{-1}$ and increment at steps of $\pm$2$\sigma$ for the VLA data; red contour levels start at $\pm$2$\sigma$, incrementing at steps of $\pm$1$\sigma$ = 0.24 mJy beam$^{-1}$.
%Right:
%Contour map of the 90.7 GHz continuum emission. The beam size is 16\farcs67$\pm
%$0\farcs69 $\times$ 7\farcs17$\pm$1\farcs60, at P.A. = -57.9$\degr$. The contour levels start at $\pm$2$\sigma$ and increment at steps of $\pm$1$\sigma$ =0.5 mJy beam$^{-1}$.\label{fig:cont}}
%\end{figure*}

>>>>

\section{HST astrometry}
We adopt the VLA 5\,GHz map as the reference coordinate frame and shift the
coordinate frame in the optical image to this one to align the emission.

Employed local phase calibrator, with positions known to $\sim$1 mas, estimate
the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
be better than 0.1", leaving aside uncertainties relating to SNR and beam size.

The astrometry of the HST images was firstly calibrated against a wider-field
optical image of the cluster which had in turn been aligned onto the FK5
coordinate system to an rms precision of ~0.2".

%The align the IRAM data (2-mm continuum and CO(J=2-1)) with the VLA 5-GHz
%continuum emission, we shifted the former to the east by BLAH" in R.A., which is
%consistent with the claimed astrometric precision of the PdBI images.

To align the optical/NIR data with the VLA 5-GHz continuum emission, we
shifted the former in Dec. by +BLAH".

\section{CO($J$ = 3 $\rightarrow$ 2) line emission}

Analysis using both set 2 and set 3 observations.

natural weighting beam size:  3.19 x 1.86 PA: 8 deg
channel width = 2x17.935 = 35.87 km/s
rms = 1.32997E-02 Jy/B/channel

 Integrated line flux = 37.509 Jy km/s over chan=[49,70] (FWZI)
%- ! Parameters and Errors:
%- ! MFIT%PAR[01]  
%- ! MFIT%PAR[02]  
%- ! MFIT%PAR[03]  
%- ! MFIT%PAR[04]  
%- velocity range [,] km/s

We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward
SMM J0939+8315 at peak flux at blah $\sigma$ signifcance of $ \sigma$ = 13.2997

mJy beam$^{-1}$.

We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
background galaxies in RXJ1131-1231. 
We extract the spectrum and fit a single-component Gaussian as shown in Figure
\ref{fig:}
yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit
is BLAH $\pm$ BLAH km s$^{-1}$.

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}	  
\caption{
CO32 line spectrum
 \label{fig:}}
\end{figure}

We made a 1.4mm continuum map using line-free channels, $\sigma$ = 8.30807E-04
Jy/B

At spatial position of CO emission, No significant continuum emission was
detected from the line-free region down to a 3$\sigma$ limit of blah mJy
(burried in noise - 
2.2 $\pm$ 3.0 mJy). Hence, we place a 3$\sigma$ upper limit of BLAH.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CO($J$ = 2 $\rightarrow$ 1) line emission}
natural weighting beam size: 4.44 x 1.95, PA 13deg
rms = ~ 1.451 mJy/ Beam/ch
velocity resolution per bin: 21.528154 km/s
source extent?

We detect dynamically resolved CO($J$ = 2 $\rightarrow$ 1) line emission toward
the background galaxies in RXJ1131-1231.

We construct the velocity-integrated (0th moment) map of the CO($J$ = 2
$\rightarrow$ 1) emission using the uv-continuum subtracted data, the
velocity-integrated 
CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ BLAH Jy km s$^{-1}$.

% upper limit on other lines 
% in the foreground galaxy -- HNC (J=2-1)

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{
0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping
Spectrum. Velocity scale w.r.t z=0.655
 \label{fig:CO21mom0}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       
\caption{
1st and 2nd order moments, clipped at 5 $\sigma$
 \label{fig:}}
\end{figure}

@@

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/ContCO21.eps}	  
\caption{CO 21 moment0 with coninuum
 \label{fig:}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/Cont2mm_5GHz_double.eps}    
\caption{VLA 5GHz continuum and PdBI 2mm continuum
 \label{fig:}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[width=0.55\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{
radio continuum contours on HST image
 \label{fig:}}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SED}
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}	 
\caption{VLA 5GHz continuum and PdBI 2mm continuum
 \label{fig:}}
\end{figure*}

\input{table_photometry_AAScustomized}
